FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2018-06-05 ECOOP18/sections/Discussion.tex
Revised Section 5

Our formalization has a simple form of abstract methods, which behave similarly to conventional methods with respect to conflicts.
Other languages may behave differently. 
For instance, in Java 8 when putting two identical abstract methods together by multiple inheritance, there is no conflict error. In Figure~\ref{fig:abstractdiamond}, we use italic $\emph{m}$ to denote abstract methods. In both cases, the Java compiler accepts the definition of $C$ and automatically merges the two inherited methods $m$ into a single one. \MIM{} behaves differently from Java in both cases.
In the \wordfork{} inheritance case (left), $C$ will have two distinct abstract methods corresponding to $A.m$ and $B.m$. 
In the diamond inheritance case, the definition of $C$ is rejected. 
There are two reasons for this difference in behaviour. Firstly, our formalization just treats abstract methods as concrete methods with an empty body, and that simplifies
the rules and proofs a lot. Secondly, and more importantly, we distinguish and treat differently conflicting methods, since they may represent different operations, even if they are abstract. Thus our model adopts a very conservative behavior rather than automatically merging 
methods by default (as done in many languages). 
\yanlin{717: we could mention that Godez (the guy maintaing java now) would
	prefer if Java behaved like our formalization but he can not for
	retrocompatibility.
	Re: where do you think is the proper place to mention this? }
Arguably, for the diamond case, as we have mentioned, it is actually an intentional conflict due to the same source $T$.
It is possible to change our model to account for other behaviors for abstract methods, but we view this as a mostly 
orthogonal change to our work, which should not affect the essence of the model presented here.

@@

\yanlin{Bruno: discussed multiple overriding and the two designs}
One non-orthogonal extension to \MIM{} could be to generalize the model to allow multiple hierarchical method overrding, meaning that, we allow overriding methods to update multiple branches instead of only one branch. It offers a more fine-grained mechanism for merging, and can be helpful to easily understand the structure of the hierarchy. Multiple overriding would be useful in the following situation, for example:

>>>>

Our formalization has a simple form of abstract methods, which behave similarly to conventional methods with respect to conflicts.
Other languages may behave differently. 
For instance, in Java 8 when putting two identical abstract methods together by multiple inheritance, there is no conflict error. In Figure~\ref{fig:abstractdiamond}, we use italic $\emph{m}$ to denote abstract methods. In both cases, the Java compiler accepts the definition of $C$ and automatically merges the two inherited methods $m$ into a single one. \MIM{} behaves differently from Java in both cases.
In the \wordfork{} inheritance case (left), $C$ will have two distinct abstract methods corresponding to $A.m$ and $B.m$. 
In the diamond inheritance case, the definition of $C$ is rejected. 
There are two reasons for this difference in behaviour. Firstly, our formalization just treats abstract methods as concrete methods with an empty body, and that simplifies
the rules and proofs a lot. Secondly, and more importantly, we distinguish and treat differently conflicting methods, since they may represent different operations, even if they are abstract. Thus our model adopts a very conservative behavior rather than automatically merging 
methods by default (as done in many languages). 
\yanlin{717: we could mention that Godez (the guy maintaing java now) would
	prefer if Java behaved like our formalization but he can not for
	retrocompatibility.
	Re: where do you think is the proper place to mention this? }
Arguably, the diamond case it is actually an intentional conflict due
to the same source $T$. Therefore our model conservatively rejects
this case.
It is possible to change our model to account for other behaviors for abstract methods, but we view this as a mostly 
orthogonal change to our work, and should not affect the essence of the model presented here.

@@

\yanlin{Bruno: discussed multiple overriding and the two designs}
One non-orthogonal extension to \MIM{} could be to generalize the
model to allow multiple hierarchical method overrding, meaning that,
we allow overriding methods to update multiple branches instead of
only one branch. This feature offers a more fine-grained mechanism for merging, and can be helpful to easily understand the structure of the hierarchy. Multiple overriding would be useful in the following situation, for example:
